\title*{Enhancing Quality of Virtual Meetings through Facial and Vocal Emotion Recognition}

\titlerunning{Enhancing Quality of Virtual Meetings through Facial \& Vocal Emotion Recognition}
% Use \titlerunning{Short Title} for an abbreviated version of
% your contribution title if the original one is too long
\author{Page, Philipp\inst{a}$_{1}$ \and
Karaus, Kilian\inst{a}$_{2}$ \and
Donner, Maximilian\inst{a}$_{3}$}
\authorrunning{Page, Karaus, Donner}

\institute{
 University of Cologne, Albertus-Magnus-Platz, 50923 Cologne, Germany
}

\maketitle
\abstract{Due to the COVID-19 pandemic, presentations via video conferencing software are part of the daily routine for many people. However, the quality of the presentations, which are used in universities to transfer knowledge but also in widespread areas of the business world, differs significantly. In order to improve meeting quality we have developed a web application allowing presenters to gather real-time metrics about the participants' moods during the meeting. In particular, the proposed system tracks the emotional state of the meeting participants and combines this data with subjective ratings. Emotional data of the audience is collected with the help of face recognition. At the same time, the systems analyzes the speaker's voice to deduce transmitted emotions. The collected data can help researchers to form hypotheses about what makes a ``good'' meeting. Additionally, presenters are able to change their presentation style during a meeting or in future meetings after performing a post hoc analysis.}

\footnotetext[1]{Corresponding author: Philipp Page, e-mail: mail@philipp-page.de}
\footnotetext[2]{Corresponding author: Kilian Karaus, e-mail: kkaraus@smail.uni-koeln.de}
\footnotetext[3]{Corresponding author: Maximilian Donner, e-mail: mdonner@smail.uni-koeln.de}
\addtocounter{footnote}{3}
